Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
added a sentence to exec/enter cond description

The condition for capabilities with read permission is
$\readCond{}$. It ensures that a read capability can only be used to
read capability safe words, by requiring that the region that governs
the part of memory that the capability grants authority over enforces
that all the words are in the value relation.  Generally speaking,
global capabilities should only depend on permanent regions. Therefore
we use the function $\var{localityReg}(g,W)$, which projects out all
active regions when $g$ is local, but only the permanent regions when
$g$ is global.

@@

The conditions $\entryCond{}$ and $\execCond{}$ are very similar and
differ only slightly. Executable capabilities can be updated to point
anywhere in memory, so they must be capability safe as a program
counter no matter where they point in memory. In contrast, enter
\lars{``capability safe as a program counter'' is a bit hard to
  understand - why not say that this is a capability one can jump to ?}
\lau{ When jumping to a capability, it becomes the program counter. A program counter is capability safe when it is the $\stder$ relation. When I say ``capability safe as a program counter'' I take it to mean being in the $\stder$-relation. }
capabilities are opaque and must be used from the address they point
to. They change permission when jumped to, so we require them to be
capability safe as a program counter when the permission is changed to
read/execute.
In both conditions, the capability must be capability safe as a
program counter in certain future worlds. If the capability is global,
then it should be capability safe as a program counter in any private
future world. This means that it can only depend on permanent regions
because temporary regions may be revoked in a private future
world. On the other hand, local capabilities must only be capability
safe in public future worlds because they may depend on temporary
regions, so we cannot expect them to function correctly as program
counters if temporary regions are revoked.

>>>>

The condition for capabilities with read permission is
$\readCond{}$. It ensures that a read capability can only be used to
read capability safe words, by requiring that the region that governs
the part of memory that the capability grants authority over enforces
that all the words are in the value relation. Generally speaking,
global capabilities should only depend on permanent regions. Therefore
we use the function $\var{localityReg}(g,W)$, which projects out all
active regions when $g$ is local, but only the permanent regions when
$g$ is global.
\todo[inline]{Do we want to mention the standard regions here? (They
  are not mentioned anywhere)}

@@

The conditions $\entryCond{}$ and $\execCond{}$ are very similar and
differ only slightly. Executable capabilities can be updated to point
anywhere in memory, so they must be capability safe as a program
counter no matter where they point in memory. In contrast, enter
\lars{``capability safe as a program counter'' is a bit hard to
  understand - why not say that this is a capability one can jump to ?}
\lau{ When jumping to a capability, it becomes the program counter. A program counter is capability safe when it is the $\stder$ relation. When I say ``capability safe as a program counter'' I take it to mean being in the $\stder$-relation. }
capabilities are opaque and must be used from the address they point
to. They change permission when jumped to, so we require them to be
capability safe as a program counter when the permission is changed to
read/execute.
In both conditions, it must be safe to jump to the capability. This
means that the capability must be capability safe as a
program counter in certain future worlds. If the capability is global,
then it should be capability safe as a program counter in any private
future world. This means that it can only depend on permanent regions
because temporary regions may be revoked in a private future
world. On the other hand, local capabilities must only be capability
safe in public future worlds because they may depend on temporary
regions, so we cannot expect them to function correctly as program
counters if temporary regions are revoked.
